No-click browsing of large hierarchical data

### 2020-03-05 paper/HCC2020/paper.tex
...

\def\SC{\textsf{\small Serencast}}
\def\SB{\textsf{\small Scrapbox}}

@@

We introduce a novel simple interaction technique for finding and browsing
data in a huge hierarchical database using only two keys or
one rotating device.
% that can generate two different signals based on the rotation direction.

We can enjoy various kinds of movies, musics, books,
etc. distribued from many service providers like Amazon and Netflix.
However, 
finding a data from the huge database is not a trivial task. Users can
either find an entry using keywords, or using a menu based
on a hierarchical structure of the database.
After successfully finding a candidate data,
the user should confirm that he wants to watch it by pressing a ``select'' button.
If the user finds that the data is not the one he wanted,
he should go back to the previous state and perform the search again.

@@

Huge amount of movies, musics, and other programs are available on the web, but
finding and viewing a program usually takes time because
(1) finding a program takes time, and
(2) a ``confirm'' operation (clicking something or typing a key)
is required for viewing the content.

@@

The confirm operations was not required on old TVs and radios,
because we could enjoy the TV and radio programs
as soon as we rotated a ``TV channel dial'' or a tuning dial of the radio.

@@

We can use the style on modern personal computers.
Using the ``\tsf{Finder.app}'' on MacOS, we can use the ``CoverFlow''\footnote{
  \tsf{https://en.wikipedia.org/wiki/Cover\_Flow}
} viewer to browse the contents in a folder
with simple swyping gestures (Figure \ref{coverflow}).

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
\caption{Cover Flow on MacOS}
\label{coverflow}
\end{figure}

We can also enjoy no-click browsing on a Finder.app windows
when we select a file in a folder and
type arrow keys for selecting other files.
The contents of the file is shown at the right as soon as
we select a file in a folder.

\begin{figure}[H]
% \centerline{\includegraphics[width=70mm,bb=0 0 1678 846]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
\centerline{\includegraphics[width=70mm,bb=0 0 839 423]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
\caption{No-click browsing on conventinal Finder mode}
\label{noclickfinder}
\end{figure}

@@

We can enjoy no-click browsing on old TVs and radios because the number of
source channels are limited.
Likely, we can enjoy no-click browsing on Finder.app when the number of files
in one folder is not very large.

No-click browsing is not popular on the GUI of personal computers.
People are used to click-based browsing on web browsers and other
information visualization systems.
People can navigate through a huge information space by
clicking links, zooming by dragging, and other GUI operations.
These techniques are useful for finding an item in a large information space,
but many clicks and dragging operations are required.
The contents of the items are usually not shown while

@@

When a user cannot use GUI, key-based interaction techniques are widely used for
finding information in hierarchical data.
%
For example, a user can find a music data by
selecting an artist from the list of artist names,
selecting an album title from the title list,
and selecting a music data from the song list.
%
Users can use two keys for choosing an entry from the list
% (e.g. selecting an artist from the artist list),
and use another key for selecting an entry and moving to the next level.
% (e.g. selecting an artist and show album titles).
It is also necessary to provide a way to go back to the previous state, and
yet another key can be used for that task.
% (e.g. showing the artist list for artist selection).
This 4-way navigation is popular on small devices
and remote controllers like AppleRemote\footnote{\textsf{http://en.wikipedia.org/wiki/Apple\_Remote}}
for selecting a song from the hierarchical data.
4-way navigation is also available on desktop software like Finder.app.

\begin{figure}[H]
\centerline{\includegraphics[width=50mm,bb=0 0 333 250]{figures/0048a5e91ddcf1d5670bd958e3c55619.jpg}}
\caption{A small device supporting 4-way navigation}
\label{rio}
\end{figure}

Using 4 keys might be okay on these devices, but it would be much better
if we could perform the navigation task using simpler dvices that have only 2 keys.
In that case, we can also use a rotating device like a disk or a wheel for the navigation,
since such devices can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
%
% We have developed a new navigation technique where only two keys are required
% for exploring large hierarchical data, and implemented the system on
% a rotating device ``Strotor''.
%
We have developed a new navigation technique called ``{Gear}'',
where users can explore a large hierarchical database by simple rotating operations.
%
Using Gear, we can enjoy no-click browsing only by typing two keys or
rotating a dial

\begin{figure}[H]
\centerline{\includegraphics[width=60mm,bb=0 0 294 110]{figures/rotation.pdf}}
\caption{Using a rotation device for generating key events.}
\label{rotation}
\end{figure}

@@

Interaction with Gear is based on the following simple principles.
Two types of operations, ``{\up}'' (up) and ``{\down}'' (down), are used for the navigation.
They can be performed either by rotating the Gear device or pressing keys.

@@

To prove that Gear is useful for selecting an entry from a very
large hierarchical database,
we have developed the ``\tsf{Serencast.com}'' service, where
users can enjoy movies, musics, and other Web services
on the browser with the Gear interface.
{\SC} is implemented in JavaScript, and runs on modern browsers

@@

When we list the URLs of Web pages of
movies and musics on a {\SB} page,
we can create a hierarchical structure from the list and
use the Gear interface to find data and browse it.
We can use \tsf{Serencast.com} service
for using the Gear interface to select a program from the
list on {\SC} pages, and automatically play it on the browser.

@@

\begin{figure}[H]
% \centerline{\includegraphics[width=80mm,bb=0 0 524 598]{figures/65b01a87b67c9a8e838a047b945f6a77.png}}
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
\caption{Showing a movie.}
\label{tiffany}
\end{figure}

@@

Since only two switches are required in the Gear interface,
various kinds of input devices can be used for Gear.
We have tried various input devices, and collected experiences.

>>>>

\def\SC{\tsf{Serencast}}
\def\SB{\tsf{Scrapbox}}

@@

We introduce a novel simple interaction technique for finding and browsing
data in a huge hierarchical database using only two keys.
% or one rotating device.
% that can generate two different signals based on the rotation direction.

We can enjoy various kinds of movies, musics, books,
etc. distributed from many service providers like Amazon and Netflix.
However, 
finding a data from the huge database is not a trivial task. Users can
either find an entry using keywords, or using a menu based
on a hierarchical structure of the database.
After successfully finding a candidate data,
the user should confirm that he wants to watch it by pressing a ``select'' button.
If the user finds that the data is not the one he wanted,
he should go back to the previous state and perform the selection again.

@@

Huge amount of movies, musics, and other programs are available on the web, but
finding and viewing a program is not easy because
(1) finding a program takes time, and
(2) a ``confirm'' operation (clicking something or typing a key)
is required for viewing the content.

@@

The confirm operations was not required on old TVs and radios,
because we could enjoy TV/radio programs
as soon as we rotated a ``TV channel dial'' or a tuning dial of the radio.

@@

We can see the non-click browsing style on personal computers.
Using the ``\tsf{Finder.app}'' on MacOS, we can use the ``CoverFlow''\footnote{
  \tsf{https://en.wikipedia.org/wiki/Cover\_Flow}
} viewer to browse the contents in a folder
with simple swyping gestures (Figure \ref{coverflow}).

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
% \centerline{\includegraphics[width=80mm,bb=0 0 803 555]{figures/5d46fb09c3c5b4baccfd68ca026ef25b.png}} % Monorail
\caption{Cover Flow on MacOS}
\label{coverflow}
\end{figure}

We can also enjoy no-click browsing on a Finder.app window
when we select a file in a folder and
type arrow keys for selecting other files.
Using the ``column view'' mode, 
the contents of the file is shown at the right side of the window
as soon as we select a file in a folder (Figure \ref{noclickfinder}).

\begin{figure}[H]
% \centerline{\includegraphics[width=70mm,bb=0 0 1678 846]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
\centerline{\includegraphics[width=70mm,bb=0 0 839 423]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
\caption{No-click browsing on the column view of Finder.app.}
\label{noclickfinder}
\end{figure}

@@

We can use no-click browsing on old TVs and radios because the number of
broadcast channels are limited.
Likewise, we can use no-click browsing on Finder.app when the number of files
in a folder is not very large.

No-click browsing is not popular on conventional GUI of personal computers.
People are used to click-based browsing on web browsers and other
information visualization systems.
People can navigate through a huge information space by
clicking links, zooming by dragging, and using other GUI techniques.
These techniques are useful for finding an item in a large information space,
but many clicks and drag operations are required.
The contents of the items are usually not shown during the search.

@@

When a user cannot use a pointing device,
key-based interaction techniques are used for
finding information in hierarchical data.
%
For example, a user can find a music data by
selecting an artist from the list of artist names,
selecting an album title from the title list,
and selecting a music title from the song list.
%
Users can use two keys for choosing an entry from the list
% (e.g. selecting an artist from the artist list),
and use another key for selecting an entry and moving to the next level.
% (e.g. selecting an artist and show album titles).
It is also necessary to use another key for going back to the previous level.
% (e.g. showing the artist list for artist selection).
This 4-way navigation is popular on small devices
and remote controllers like AppleRemote\footnote{\textsf{http://en.wikipedia.org/wiki/Apple\_Remote}}
for selecting a song from the hierarchical data.
4-way navigation is also available on the column view of Finder.app.

\begin{figure}[H]
\centerline{
  \includegraphics[width=30mm,bb=0 0 333 250]{figures/0048a5e91ddcf1d5670bd958e3c55619.jpg}
  \includegraphics[width=30mm,bb=0 0 551 551]{figures/70c036b24525c6cace9955b24152e97e.jpg}
  }
\caption{Small devices supporting 4-way navigation}
\label{rio}
\end{figure}

Using 4 keys might be okay on these devices, but it would be much better
if we could perform the navigation task using simpler dvices that have only two keys.
In that case, we can use a rotating device like a disk or a wheel for the navigation,
since such devices can generate 2 signals based on the rotation direction.

We have developed a new navigation technique called ``{Gear}'' for no-click browsing,
where users can explore a large hierarchical database by using only two keys.

\comment{
\begin{figure}[H]
\centerline{\includegraphics[width=60mm,bb=0 0 294 110]{figures/rotation.pdf}}
\caption{Using a rotation device for generating key events.}
\label{rotation}
\end{figure}
}

@@

Interaction with Gear is based on the following simple principles.
Two types of operations,
``{\up}'' (up) and ``{\down}'' (down), are used for the navigation.
They can be performed either by pressing keys or rotating a dial.

@@

To prove that Gear is useful for selecting an entry from a very
large hierarchical database,
we have developed the ``{\SC}'' service, where
users can enjoy movies, musics, and other Web services
on the browser with the Gear interface.
{\SC} is implemented in JavaScript, and runs on modern browsers

@@

When we list the URLs of Web pages of
movies and musics on a {\SB} page,
we can create a hierarchical structure from the list and
use the Gear interface to find data and browse it.
We can use {\SC} service
for using the Gear interface to select a program from the
list on {\SC} pages, and automatically play it on the browser.

@@

\begin{figure}[H]
% \centerline{\includegraphics[width=80mm,bb=0 0 524 598]{figures/65b01a87b67c9a8e838a047b945f6a77.png}}
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
\caption{Showing ``Breakfast at Tiffany's''.}
\label{tiffany}
\end{figure}

@@

Since only two switches are required in the Gear interface,
various kinds of input devices can be used for Gear.
We have tried some input devices and collected experiences.
